\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 lang-design.tex
edits in FMLTT sec
Some Comments.

\subsection{Composing Families as Mixins}

@@

Families can be readily reused to construct larger extensions that
\emph{mix in}~\cite{mixin-1990} the functionalities of the individual
families.
A family like \lsti{STLCFix} can be viewed as a family-to-family functor---%
and hence a mixin, in the sense of \cite{flatt1998mixin}---that
transforms any family providing the base STLC functionalities into a new
family additionally supporting fixpoints.
%\EDJ{I feel this paragraph will cause more confusion---because it is inheritance judgement/linkage transformer being mixed in, not family itself. Conceptually not distinguishing family and linkage transfomer will make reader wonder what this magic black box here actually is}

@@

Mixin composition is a form of multiple inheritance, which may lead to
name conflicts in general.
\Lang requires the programmer to resolve conflicts by
explicitly overriding conflicted fields.

@@

\subsection{Injectivity and Disjointness of Constructors via Partial Recursors}

>>>>

\subsection{Composing Families as Mixins}
\label{sec:mixin}

@@

Families can be readily reused to construct larger extensions that
\emph{mix in}~\cite{mixin-1990} the functionalities of the individual
families.
A family like \lsti{STLCFix} can be viewed as a family-to-family functor\EDJ{The reader might be confused why look at them as functor, as the parent seems unchanged. One insight is that the parent of nested family, in Zhang OOPSLA 2017, is late-bound. Thus it has to be a functor. }---%
and hence a mixin, in the sense of \cite{flatt1998mixin}---that
transforms any family providing the base STLC functionalities into a new
family additionally supporting fixpoints.
%\EDJ{I feel this paragraph will cause more confusion---because it is inheritance judgement/linkage transformer being mixed in, not family itself. Conceptually not distinguishing family and linkage transfomer will make reader wonder what this magic black box here actually is}

@@

Mixin composition is a form of multiple inheritance, which may lead to
name conflicts in general.\EDJ{Only name conflicts on overridable fields can be resolved like this. Name/definition conflicts for normal fields cannot be resolved (cannot be mixed in). }
\Lang requires the programmer to resolve conflicts by
explicitly overriding conflicted fields.

@@

\subsection{Injectivity and Disjointness of Constructors via Partial Recursors}
\label{sec:prec}
